\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

\usepackage{marginnote} % For margin years
\newcommand{\years}[1]{\marginnote{\scriptsize #1}} % New command for including margin years
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt} % Slightly increase the distance of the margin years from the contant
\reversemarginpar

\usepackage{tabu}
%\usepackage{etaremune}

% Set your name here
\def\name{Chengxin Xu}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
%% \def\footerlink{http://jblevins.org/projects/cv-template/}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {public management, nonprofit management},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\bfseries\large}
\subsectionfont{\rmfamily\bfseries\large}
\subsubsectionfont{\rmfamily\normalsize}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
% {\huge \name}

% Alternatively, print name centered and bold:
\centerline{\huge \bf \name}

\begin{center}
  Curriculum Vitae
\end{center}


\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    %%\href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  \href{https://www.seattleu.edu/artsci/departments/ips/}{Seattle University} \\
  Institute of Public Service \\
  901 12th Avenue, Casey 210-09 \\ 
  Seattle, WA 98122
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: & (206) 296-5430 \\
    Home: & (862) 872-6700 \\
    Email: & \href{mailto:cxu1@seattleu.edu}{\tt cxu1@seattleu.edu} \\
    Website: & \href{https://cxuchengxin.github.io/website/}{\tt https://cxuchengxin.github.io/website/} \\
  \end{tabular}
\end{minipage}


%\section*{Personal}

%\begin{itemize}
%\item Born on September 29, 1895.
%\item United States Citizen.
%\end{itemize}
%\bigskip

\section*{POSITION \& AFFILIATIONS}
\begin{tabular}{ p{2.5cm} p{13cm} }
	From 2019 & \textbf{Seattle University, Institute of Public Service} \\
	& \it{Assistant professor}

\end{tabular}

\bigskip

\section*{EDUCATION}

\begin{tabular}{ p{2.5cm} p{13cm} }
   2019 & \textbf{Rutgers University-Newark, School of Public Affairs and Administration} \\
   & PhD in \it{Public Administration} \\
   &{\it Dissertation}: Financing Social Missions: Essays on the Role of Commercialization in Nonprofit Social Service Organizations in the U.S.\\
   &\\
   2015 & \textbf{Rutgers University-Newark} \\
   &M.P.A.\\
   & \\
   2010 & \textbf{East China University of Political Science and Law} \\
   &BA in \it{Law}

\end{tabular}


\bigskip

\section*{RESEARCH INTERESTS}
\begin{itemize}
\item Public \& Nonprofit Management, Judgment and Decision Making in Public and Nonprofit Management, Methodology.
\end{itemize}

\bigskip
%\section*{Employment}

%\begin{itemize}
%\item Stanford University 1927--1931.
%\item Columbia University 1931--1946.
%\item University of North Carolina, 1946--1973.
%\end{itemize}


\section*{PUBLICATIONS}
\subsection*{Journal Articles}

\begin{itemize}

\item \textbf{Xu, Chengxin}. and Li, Huafang., Resource Publicness Matters in Organizational Perceptions. (2021). Forthcoming at {\it Public Administration Review}.

\item \textbf{Xu, Chengxin}. and Kim, Mirae. (2021). Unpacking Nonprofit Autonomy-Interdependence Paradox in Collaborative Relationships. {\it American Review of Public Administration}. Online first.

\item Favero, Nathan, Jilke, Sebastian, Wolfson, Julia A., \textbf{Xu, Chengxin} and Young, Matthew. (2020) Messenger effects in COVID-19 communication: Does the level of government matter? {\it Health Policy OPEN}, 100027. 

\item \textbf{Xu, Chengxin}. (2020). The Perceived Differences: The Sector Stereotypes of Social Service Providers. {\it Nonprofit and Voluntary Sector Quarterly}.	{\it 49}(6), 1293-1310.

\item Li, Huafang, \textbf{Xu, Chengxin}., and McDougle, Lindsey. (2019). Philanthropy Can Be Learned: A Qualitative Study of Student Experiences in Experiential Philanthropy Courses. {\it Philanthropy and Education}. {\it 2}(2), 29-52.

\item Jilke, Sebastian., Lu, Jiahuan., \textbf{Xu, Chengxin}., and Shinohara, Shugo. (2019). Using Large Scale Social Media Experiments in Public Administration: Assessing Charitable Consequences of Government Funding to Nonprofits. {\it Journal of Public Administration Research and Theory}. {\it 29}(4), 627-639.

\item Lu, Jiahuan. and \textbf{Xu, Chengxin}. (2018). Complementary or Supplementary? The Relationship between Government Size and Nonprofit Sector Size. {\it VOLUNTAS}. {\it 29}(3), 454-469.

\item McDougle, Lindsey, McDonald, D., McIntyre Miller, W., Li, Hhuafang, and \textbf{Xu, Chengxin}. (2017). Can Philanthropy be Taught? {\it Nonprofit and Voluntary Sector Quarterly}. {\it 46}(2), 330-351. 

\end{itemize}

\subsection*{Book Chapters and Others}
\begin{itemize}
	
\item \textbf{Xu, Chengxin}., Li, Huafang, and McDougle, Lindsey (2018) Experiential Philanthropy in {\it Global Encyclopaedia of Public Administration, Public Policy, and Governance}. Springer Publication.

\end{itemize}

\subsection*{Manuscripts Under Review}
\begin{itemize}
	
\item Liu, Yixin and \textbf{Xu, Chengxin}. De-stereotyping Public Performance Evaluation. Under review at {\it Public Administration Review}.

\item Vogel, Dominik, and \textbf{Xu, Chengxin}. Everything hacked? What is the Evidential Value of the Experimental Public Administration Literature? Invited to revise and resubmit at {\it Journal of Behavioral Public Administration}.

\item \textbf{Xu, Chengxin} and Liu, Yixin, Does Labeling COVID-19 as “Chinese Virus” Trigger Perceived Foreign Threats and
Reduce the Blame? (preprint: \href{https://psyarxiv.com/j4t2r/}{\tt https://psyarxiv.com/j4t2r/}). Invited to revise and resubmit at {\it Journal of Behavioral Public Administration}.

\end{itemize}


\subsection*{Manuscripts in Preparation}
\begin{itemize}

\item \textbf{Xu, Chengxin}. Technology Transfer, Research Commercialization, and the Credit Ratings of Nonprofit Universities ({\it Finalizing}).

\item \textbf{Xu, Chengxin}. Relational Fitness: A Model for Sector Differences ({\it Data Collection}).

\item \textbf{Xu, Chengxin}. A Field Experiment on Discrimination against Immigrants in the U.S. Health Care Market ({\it Research Design}).

\end{itemize}

\bigskip

\section*{CONFERENCE ACTIVITIES}
\subsection*{Panels Organized}
\subsubsection*{2018}
\begin{itemize}
\item "Opportunities and Challenges: Experiments in Nonprofit and Philanthropy Research" Association for Research on Nonprofit Organizations and Voluntary Action (ARNOVA) Annual Conference, Austin, TX.
\end{itemize}

\subsection*{Papers Presented}
\subsubsection*{2020}
\begin{itemize}

\item ``Relational Fitness: A Model for Perceived Sector Difference". Association for Research on Nonprofit Organizations and Voluntary Action (ARNOVA) Annual Conference, Online.
	
\item ``Destereotyping Public Performance Evaluation". European Group for Public Administration (EGPA) e-Conference. (with Yixin Liu)
	
\end{itemize}

\subsubsection*{2019}
\begin{itemize}

\item "Major Revenue Cues Sector Stereotypes" Association for Research on Nonprofit Organizations and Voluntary Action (ARNOVA) Annual Conference, San Diego, CA. (with Huafang Li)

\item "Nudged by the Public: Social Influence Affects Citizens' Judgments on Policy Performance" Public Management Research Conference, Chapel Hill, NC. (with Yixin Liu)

\item "The Perceived Difference: The Sector Stereotype of Social Service Providers" Public Management Research Conference, Chapel Hill, NC.

\end{itemize}

\subsubsection*{2018}
\begin{itemize}

\item "Sector Information and Legitimacy for Social Enterprises: Insights from An Experiment" Association for Research on Nonprofit Organizations and Voluntary Action (ARNOVA) Annual Conference, Austin, TX. 

\item "Unpacking Interorganizational Collaboration: Does it Hinder Organizational Autonomy?" Association for Research on Nonprofit Organizations and Voluntary Action (ARNOVA) Annual Conference, Austin, TX. (with Mirae Kim) 

\item "Social Contagion in Policy Performance Evaluation: Evidence from a Survey Experiment" Association for Public Policy Analysis \& Management (APPAM) Fall Research Conference, Washington, D.C. 

\item "Nonprofits Are Rabbits and For-profits Are Wolves? A Survey Experiment in the Social Enterprise Zoo" Social Entrepreneurship/Enterprise Section (SEES) Research Colloquium, ARNOVA, San Diego, CA.

\end{itemize}

\subsubsection*{2017}
\begin{itemize}
\item "Can Nonprofit Organizations Sustain Financial Autonomy in Collaboration?" Association for Research on Nonprofit Organizations and Voluntary Action (ARNOVA) Annual Conference, Grand Rapids, MI. (with Mirae Kim)

\item "Government Funding and Private Donations: Crowding-in Versus Crowding-out in the Context of a Big Data Experiment." Association for Research on Nonprofit Organizations and Voluntary Action (ARNOVA) Annual Conference, Grand Rapids, MI. (with Sebastian Jilke, Jiahuan Lu, Shugo Shinohara)

\item "To Visualize Nonprofit Organization Research in China: A Co-Citation Network Analysis." Association for Research on Nonprofit Organizations and Voluntary Action (ARNOVA) Asia Conference, Beijing, China.

\end{itemize}

\subsubsection*{2016}
\begin{itemize}

\item "Exploring the Impact of Government Funding on the Organizational Autonomy of Human Services Nonprofits." Association for Research on Nonprofit Organizations and Voluntary Action (ARNOVA) Annual Conference, Washington, D.C.

\end{itemize}

\bigskip

\section*{TEACHING EXPERIENCE}
\subsection*{Seattle University}
\subsubsection*{Graduate level}
\begin{itemize}
	\item Research Design
	\item Foundations of Public Administration
	\item Economic Analysis
\end{itemize}

\subsection*{Rutgers University-Newark}
\subsubsection*{Undergraduate level}
\begin{itemize}	
\item Introduction to Nonprofit Administration
\end{itemize}

\subsubsection*{Graduate level}
\begin{itemize}	
\item Applied Research Design
\end{itemize}

\subsubsection*{Doctoral level}
\begin{itemize}	
\item Guest Lecture: Replication, for Selected Topics in Public Administration: Experimental and Behavioral Public Administration
\end{itemize}

\bigskip


\section*{AWARDS AND HONORS}
\begin{itemize}
	
\item {\it Student Assistantship Award (Competitive)}, College of Art \& Science, Seattle University, 2020-21. 
	
\item {\it Outstanding Ph.D Student}, School of Public Affairs and Administration, Rutgers-Newark, 2019

\item {\it Hayek Fund}, Institute for Humane Studies at George Mason University ({\it \$700}), 2018

\item {\it Dissertation Fellowship}, Rutgers University ({\it \$20,000}), 2018

\item {\it Conference Scholarships and Travel Grants}, Association for Research on Nonprofit Organizations and Voluntary Action (ARNOVA), 2016, 2017

\item {\it Diversity Scholar}, Association for Research on Nonprofit Organizations and Voluntary Action (ARNOVA), 2016, 2017

\item {\it Certificate: Effective Teaching Practices}, American Council on Education, 2017

\item {\it Teaching Assistant and Graduate Assistant Professional Development Fund Award}, Rutgers University-Newark, 2017, 2018

\item {\it Teaching Assistant Scholarship}, School of Public Affairs and Administration, Rutgers University, 2015-2018

\item {\it Pi Alpha Alpha}, National Public Administration Honorary in the U.S., 2014

\end{itemize}

\bigskip


\section*{GRANTS}
\begin{itemize}
	
\item {\it The University Classroom as a Philanthropic Learning Laboratory}, Rutgers University Chancellor's Seed Grants Program ({\it \$50,000}), Co-PI. 2016-2017

\end{itemize}

\bigskip

\section*{ACADEMIC SERVICE}
\subsection*{Service to the Profession}
\begin{itemize}
	
\item Track Chair, Association for Research on Nonprofit Organizations and Voluntary Action (ARNOVA) Annual Conference, 2020

\item Assistant Editor, {\it Chinese Public Administration Review}, 2016-

\item Editor, \href{https://pagateway.newark.rutgers.edu/}{\it Public Administration Gateway}, 2013-2016

\end{itemize}

\subsection*{Manuscript Reviewer}
\begin{itemize}
	
\item {\it Nonprofit and Voluntary Sector Quarterly, Public Management Review, Nonprofit Management and Leadership, Journal of Public Administration Research and Theory, Journal of Behavioral Public Administration, Journal of Nonprofit and Public Affairs, Chinese Public Administration Review.}

\end{itemize}

\bigskip

\section*{PROFESSIONAL MEMBERSHIPS}
\begin{itemize}
	
\item Public Management Research Association ({\it PMRA})
	
\item Association for Research on Nonprofit Organizations and Voluntary Action ({\it ARNOVA})

\item Society for Judgment and Decision Making ({\it SJDM})

\end{itemize}

\bigskip

%\section*{REFERENCES}
%\begin{minipage}{0.45\linewidth}
%    \textbf{Dr. Lindsey McDougle}\\
%    Associate Professor \\
%    Rutgers University-Newark\\
%    111 Washington St., Newark, NJ 07102\\
%    Phone: (973)-353-5336 \\
%    Email: \href{mailto: lindsey.mcdougle@rutgers.edu}{\tt  lindsey.mcdougle@rutgers.edu} \\
%\end{minipage}
%\begin{minipage}{0.45\linewidth}
%    \textbf{Dr. Sebastian Jilke}\\
%    Assistant Professor \\
%    Rutgers University-Newark\\
%    111 Washington St., Newark, NJ 07102\\
%    Phone: (973)-353-3706 \\
%    Email: \href{mailto: sebastian.jilke@rutgers.edu}{\tt  sebastian.jilke@rutgers.edu} \\
%\end{minipage}

%\begin{minipage}{0.45\linewidth}
%    \textbf{Dr. Marc Holzer}\\
%    Distinguished Professor \\
%    Suffolk University-Boston\\
%    73 Tremont St., Boston, MA 02108\\
%    Phone: (617)-573-8316 \\
%    Email: \href{mailto: mholzer@suffolk.edu}{\tt  mholzer@suffolk.edu} \\
%\end{minipage}
%\begin{minipage}{0.45\linewidth}
%    \textbf{Dr. Curtis Child}\\
%    Associate Professor \\
%    Brigham Young University\\
%    Provo, UT 84602\\
%    Phone: (801)-422-8079 \\
%    Email: \href{mailto: cchild@byu.edu}{\tt  cchild@byu.edu} \\
%\end{minipage}

%\begin{minipage}{0.45\linewidth}
%    \textbf{Dr. Cleopatra Charles}\\
%    Associate Professor \\
%    Rutgers University-Newark\\
%    111 Washington St., Newark, NJ 07102\\
%    Phone: (973)-353-3677 \\
%    Email: \href{mailto: cleopatra.charles@rutgers.edu}{\tt  cleopatra.charles@rutgers.edu} \\
%\end{minipage}

\end{document}